The benefits of reporting critical effect size values\footnote{The manuscript as been posted as a pre-print and has not yet undergone peer-review.}

### 2025-03-04 paper/paper.tex
adding equations with only sample size in the table

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother
\usepackage{xcolor}
\newcommand{\bfilippo}{\color{blue}}
\newcommand{\efilippo}{\color{black}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={The benefits of reporting critical effect size values},
  pdfauthor={Ambra Perugini1, Filippo Gambarota1, Enrico Toffalini2, Daniël Lakens3, Massimiliano Pastore1, Livio Finos4, Psicostat1, \& Gianmarco Altoè1},
  pdflang={en-EN},
  pdfkeywords={critical effect size values, statistical significance, hypothesis testing, effect sizes},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\hypertarget{small-sample-sizes-and-uncertain-sample-size-determination}{%
\subsection{Small Sample Sizes and Uncertain Sample Size Determination}\label{small-sample-sizes-and-uncertain-sample-size-determination}}

@@

\begin{table}[H]
\centering
\caption{\label{tab:eqsummary}Summary of the critical effect size equations, see text for details.}
\centering
\begin{tabular}[t]{ll}
\toprule
\textbf{Model} & \textbf{Equation}\\
\midrule
One-sample t-test & $d_c = \frac{t_c \times \mbox{SE}_b}{s}$\\
\cmidrule{1-2}
 & $d_c = \frac{t_c \times \mbox{SE}_b}{s_p}$\\
\cmidrule{2-2}
\multirow{-2}{*}{\raggedright\arraybackslash Paired t-test} & $d_{z_c} = \frac{t_c \times \mbox{SE}_b}{s_D}$\\
\cmidrule{1-2}
Between-sample t-test & $d_c = \frac{t_c \times \mbox{SE}_b}{s_p}$\\
\cmidrule{1-2}
 & $r_c = \frac{t_c}{\sqrt{n - 2 + t^2_c}}$\\
\cmidrule{2-2}
\multirow{-2}{*}{\raggedright\arraybackslash Correlation} & $r_{z_c} = \frac{z_c}{\sqrt{n - 3}}$\\
\cmidrule{1-2}
Meta-analysis/Regression & $\beta_c = t_c \times \mbox{SE}_{\beta}$\\
\bottomrule
\end{tabular}
\end{table}

@@

\hypertarget{examples-in-r}{%
\section{Examples in R}\label{examples-in-r}}

@@

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-altoe2020enhancing}{}}%
Altoè, G., Bertoldo, G., Zandonella Callegher, C., Toffalini, E., Calcagnı̀, A., Finos, L., \& Pastore, M. (2020). Enhancing statistical inference in psychological research via prospective and retrospective design analysis. \emph{Frontiers in Psychology}, \emph{10}, 499756.

\leavevmode\vadjust pre{\hypertarget{ref-apa2020publication}{}}%
American Psychological Association. (2020). \emph{Publication manual of the american psychological association} (7th ed.). American Psychological Association. \url{https://doi.org/10.1037/0000165-000}

\leavevmode\vadjust pre{\hypertarget{ref-anvari2023not}{}}%
Anvari, F., Kievit, R., Lakens, D., Pennington, C. R., Przybylski, A. K., Tiokhin, L., Wiernik, B. M., \& Orben, A. (2023). Not all effects are indispensable: Psychological science requires verifiable lines of reasoning for whether an effect matters. \emph{Perspectives on Psychological Science}, \emph{18}(2), 503--507.

\leavevmode\vadjust pre{\hypertarget{ref-bakan1967method}{}}%
Bakan, D. (1967). On method: Toward a reconstruction of psychological investigation. \emph{(No Title)}.

\leavevmode\vadjust pre{\hypertarget{ref-borenstein2021introduction}{}}%
Borenstein, M., Hedges, L. V., Higgins, J. P., \& Rothstein, H. R. (2021). \emph{Introduction to meta-analysis}. John wiley \& sons.

\leavevmode\vadjust pre{\hypertarget{ref-boring1919mathematical}{}}%
Boring, E. G. (1919). Mathematical vs. Scientific significance. \emph{Psychological Bulletin}, \emph{16}(10), 335.

\leavevmode\vadjust pre{\hypertarget{ref-Bowley1928-yt}{}}%
Bowley, A. L. (1928). The standard deviation of the correlation coefficient. \emph{Journal of the American Statistical Association}, \emph{23}, 31. \url{https://doi.org/10.2307/2277400}

\leavevmode\vadjust pre{\hypertarget{ref-byers2020building}{}}%
Byers-Heinlein, K., Bergmann, C., Davies, C., Frank, M. C., Hamlin, J. K., Kline, M., Kominsky, J. F., Kosie, J. E., Lew-Williams, C., Liu, L., et al. (2020). Building a collaborative psychological science: Lessons learned from ManyBabies 1. \emph{Canadian Psychology/Psychologie Canadienne}, \emph{61}(4), 349.

\leavevmode\vadjust pre{\hypertarget{ref-chow1988significance}{}}%
Chow, S. L. (1988). Significance test or effect size? \emph{Psychological Bulletin}, \emph{103}(1), 105.

\leavevmode\vadjust pre{\hypertarget{ref-cohen1994}{}}%
Cohen, J. (1994). The earth is round (p \textless{} .05). \emph{American Psychologist}, \emph{49}(12), 997--1003.

\leavevmode\vadjust pre{\hypertarget{ref-cortina1997logic}{}}%
Cortina, J. M., \& Dunlap, W. P. (1997). On the logic and purpose of significance testing. \emph{Psychological Methods}, \emph{2}(2), 161.

\leavevmode\vadjust pre{\hypertarget{ref-cumming2012statistical}{}}%
Cumming, G., Fidler, F., Kalinowski, P., \& Lai, J. (2012). The statistical recommendations of the american psychological association publication manual: Effect sizes, confidence intervals, and meta-analysis. \emph{Australian Journal of Psychology}, \emph{64}(3), 138--146.

\leavevmode\vadjust pre{\hypertarget{ref-Fisher1915-ks}{}}%
Fisher, R. A. (1915). Frequency distribution of the values of the correlation coefficient in samples from an indefinitely large population. \emph{Biometrika}, \emph{10}, 507. \url{https://doi.org/10.2307/2331838}

\leavevmode\vadjust pre{\hypertarget{ref-Fisher1921-qz}{}}%
Fisher, R. A. (1921). On the "probable error" of a coefficient of correlation deduced from a small sample. \emph{Metron}.

\leavevmode\vadjust pre{\hypertarget{ref-funder2019evaluating}{}}%
Funder, D. C., \& Ozer, D. J. (2019). Evaluating effect size in psychological research: Sense and nonsense. \emph{Advances in Methods and Practices in Psychological Science}, \emph{2}(2), 156--168.

\leavevmode\vadjust pre{\hypertarget{ref-Gelman2008-zp}{}}%
Gelman, A. (2008). Scaling regression inputs by dividing by two standard deviations. \emph{Statistics in Medicine}, \emph{27}, 2865--2873. \url{https://doi.org/10.1002/sim.3107}

\leavevmode\vadjust pre{\hypertarget{ref-gigerenzer2004null}{}}%
Gigerenzer, G., Krauss, S., \& Vitouch, O. (2004). The null ritual. \emph{The Sage Handbook of Quantitative Methodology for the Social Sciences}, 391--408.

\leavevmode\vadjust pre{\hypertarget{ref-Gross2023-fl}{}}%
Groß, J., \& Möller, A. (2023). A note on cohen's d from a partitioned linear regression model. \emph{Journal of Statistical Theory and Practice}, \emph{17}. \url{https://doi.org/10.1007/s42519-023-00323-w}

\leavevmode\vadjust pre{\hypertarget{ref-hagen1997praise}{}}%
Hagen, R. L. (1997). \emph{In praise of the null hypothesis statistical test.}

\leavevmode\vadjust pre{\hypertarget{ref-haig2017tests}{}}%
Haig, B. D. (2017). Tests of statistical significance made sound. \emph{Educational and Psychological Measurement}, \emph{77}(3), 489--506.

\leavevmode\vadjust pre{\hypertarget{ref-Hedges1981-za}{}}%
Hedges, L. V. (1981). Distribution theory for glass's estimator of effect size and related estimators. \emph{Journal of Educational and Behavioral Statistics: A Quarterly Publication Sponsored by the American Educational Research Association and the American Statistical Association}, \emph{6}, 107--128. \url{https://doi.org/10.3102/10769986006002107}

\leavevmode\vadjust pre{\hypertarget{ref-hedges1984estimation}{}}%
Hedges, L. V. (1984). Estimation of effect size under nonrandom sampling: The effects of censoring studies yielding statistically insignificant mean differences. \emph{Journal of Educational Statistics}, \emph{9}(1), 61--85.

\leavevmode\vadjust pre{\hypertarget{ref-hodges1954matching}{}}%
Hodges, J., \& Lehmann, E. (1954). Matching in paired comparisons. \emph{The Annals of Mathematical Statistics}, \emph{25}(4), 787--791.

\leavevmode\vadjust pre{\hypertarget{ref-jarke2022roadmap}{}}%
Jarke, H., Anand-Vembar, S., Alzahawi, S., Andersen, T. L., Bojanić, L., Carstensen, A., Feldman, G., Garcia-Garzon, E., Kapoor, H., Lewis, S., et al. (2022). A roadmap to large-scale multi-country replications in psychology. \emph{Collabra: Psychology}, \emph{8}(1), 57538.

\leavevmode\vadjust pre{\hypertarget{ref-kirk1996practical}{}}%
Kirk, R. E. (1996). Practical significance: A concept whose time has come. \emph{Educational and Psychological Measurement}, \emph{56}(5), 746--759.

\leavevmode\vadjust pre{\hypertarget{ref-kramer2014experimental}{}}%
Kramer, A. D., Guillory, J. E., \& Hancock, J. T. (2014). Experimental evidence of massive-scale emotional contagion through social networks. \emph{Proceedings of the National Academy of Sciences of the United States of America}, \emph{111}(24), 8788.

\leavevmode\vadjust pre{\hypertarget{ref-krueger2001null}{}}%
Krueger, J. (2001). Null hypothesis significance testing: On the survival of a flawed method. \emph{American Psychologist}, \emph{56}(1), 16.

\leavevmode\vadjust pre{\hypertarget{ref-lakens2013calculating}{}}%
Lakens, D. (2013). Calculating and reporting effect sizes to facilitate cumulative science: A practical primer for t-tests and ANOVAs. \emph{Frontiers in Psychology}, \emph{4}, 62627.

\leavevmode\vadjust pre{\hypertarget{ref-lakens2021practical}{}}%
Lakens, D. (2021). The practical alternative to the p value is the correctly used p value. \emph{Perspectives on Psychological Science}, \emph{16}(3), 639--648.

\leavevmode\vadjust pre{\hypertarget{ref-lakens2022sample}{}}%
Lakens, D. (2022). Sample size justification. \emph{Collabra: Psychology}, \emph{8}(1), 33267.

\leavevmode\vadjust pre{\hypertarget{ref-mesquida2024effect}{}}%
Mesquida, C., \& Lakens, D. (2024). Is the effect large enough to matter? Why exercise physiologists should interpret effect sizes meaningfully: A reply to williams et al.(2023). \emph{Journal of Physiology}, \emph{602}(1).

\leavevmode\vadjust pre{\hypertarget{ref-miller2017hypothesis}{}}%
Miller, J. (2017). Hypothesis testing in the real world. \emph{Educational and Psychological Measurement}, \emph{77}(4), 663--672.

\leavevmode\vadjust pre{\hypertarget{ref-morris2002combining}{}}%
Morris, S. B., \& DeShon, R. P. (2002). Combining effect size estimates in meta-analysis with repeated measures and independent-groups designs. \emph{Psychological Methods}, \emph{7}(1), 105.

\leavevmode\vadjust pre{\hypertarget{ref-moshontz2018psychological}{}}%
Moshontz, H., Campbell, L., Ebersole, C. R., IJzerman, H., Urry, H. L., Forscher, P. S., Grahe, J. E., McCarthy, R. J., Musser, E. D., Antfolk, J., et al. (2018). The psychological science accelerator: Advancing psychology through a distributed collaborative network. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(4), 501--515.

\leavevmode\vadjust pre{\hypertarget{ref-nickerson2000null}{}}%
Nickerson, R. S. (2000). Null hypothesis significance testing: A review of an old and continuing controversy. \emph{Psychological Methods}, \emph{5}(2), 241.

\leavevmode\vadjust pre{\hypertarget{ref-nunnally1960place}{}}%
Nunnally, J. (1960). The place of statistics in psychology. \emph{Educational and Psychological Measurement}, \emph{20}(4), 641--650.

\leavevmode\vadjust pre{\hypertarget{ref-orben_crud_2020}{}}%
Orben, A., \& Lakens, D. (2020). Crud ({Re}){Defined}. \emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(2), 238--247. \url{https://doi.org/10.1177/2515245920917961}

\leavevmode\vadjust pre{\hypertarget{ref-riesthuis2024simulation}{}}%
Riesthuis, P. (2024). Simulation-based power analyses for the smallest effect size of interest: A confidence-interval approach for minimum-effect and equivalence testing. \emph{Advances in Methods and Practices in Psychological Science}, \emph{7}(2), 25152459241240722.

\leavevmode\vadjust pre{\hypertarget{ref-Satterthwaite1946-aq}{}}%
Satterthwaite, F. E. (1946). An approximate distribution of estimates of variance components. \emph{Biometrics Bulletin}, \emph{2}, 110. \url{https://doi.org/10.2307/3002019}

\leavevmode\vadjust pre{\hypertarget{ref-serlin1985rationality}{}}%
Serlin, R. C., \& Lapsley, D. K. (1985). \emph{Rationality in psychological research: The good-enough principle.}

\leavevmode\vadjust pre{\hypertarget{ref-sirois2023pupil}{}}%
Sirois, S., Brisson, J., Blaser, E., Calignano, G., Donenfeld, J., Hepach, R., Hochmann, J.-R., Kaldy, Z., Liszkowski, U., Mayer, M., et al. (2023). The pupil collaboration: A multi-lab, multi-method analysis of goal attribution in infants. \emph{Infant Behavior and Development}, \emph{73}, 101890.

\leavevmode\vadjust pre{\hypertarget{ref-szucs2017empirical}{}}%
Szucs, D., \& Ioannidis, J. P. (2017). Empirical assessment of published effect sizes and power in the recent cognitive neuroscience and psychology literature. \emph{PLoS Biology}, \emph{15}(3), e2000797.

\leavevmode\vadjust pre{\hypertarget{ref-transue2019apa}{}}%
Transue, B. (2019). \emph{APA style 7th edition}.

\leavevmode\vadjust pre{\hypertarget{ref-Viechtbauer2007-tq}{}}%
Viechtbauer, W. (2007). Approximate confidence intervals for standardized effect sizes in the two-independent and two-dependent samples design. \emph{Journal of Educational and Behavioral Statistics: A Quarterly Publication Sponsored by the American Educational Research Association and the American Statistical Association}, \emph{32}, 39--60. \url{https://doi.org/10.3102/1076998606298034}

\leavevmode\vadjust pre{\hypertarget{ref-Viechtbauer2015-tn}{}}%
Viechtbauer, W., López-López, J. A., Sánchez-Meca, J., \& Marín-Martínez, F. (2015). A comparison of procedures to test for moderators in mixed-effects meta-regression models. \emph{Psychological Methods}, \emph{20}, 360--374. \url{https://doi.org/10.1037/met0000023}

\leavevmode\vadjust pre{\hypertarget{ref-weiss2014spatial}{}}%
Weiss, A. H., Biron, T., Lieder, I., Granot, R. Y., \& Ahissar, M. (2014). Spatial vision is superior in musicians when memory plays a role. \emph{Journal of Vision}, \emph{14}(9), 18--18.

\leavevmode\vadjust pre{\hypertarget{ref-Welch1947-wh}{}}%
Welch, B. L. (1947). The generalization of {``student's''} problem when several different population variances are involved. \emph{Biometrika}, \emph{34}, 28. \url{https://doi.org/10.2307/2332510}

\leavevmode\vadjust pre{\hypertarget{ref-wilson2020science}{}}%
Wilson, B. M., Harris, C. R., \& Wixted, J. T. (2020). Science is not a signal detection problem. \emph{Proceedings of the National Academy of Sciences}, \emph{117}(11), 5559--5567.

>>>>

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother
\usepackage{xcolor}
\newcommand{\bfilippo}{\color{blue}}
\newcommand{\efilippo}{\color{black}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={The benefits of reporting critical effect size values},
  pdfauthor={Ambra Perugini1, Filippo Gambarota1, Enrico Toffalini2, Daniël Lakens3, Massimiliano Pastore1, Livio Finos4, Psicostat1, \& Gianmarco Altoè1},
  pdflang={en-EN},
  pdfkeywords={critical effect size values, statistical significance, hypothesis testing, effect sizes},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\subsection{Small Sample Sizes and Uncertain Sample Size Determination}\label{small-sample-sizes-and-uncertain-sample-size-determination}

@@

\begin{table}[H]

\caption{\label{tab:eqsummary}Summary of the critical effect size equations, see text for details. When possible, we also included the equation to calculate the critical effect size without computing the standard error. For the paired t-test, this is feasible when using the standard deviation of differences. For the two-sample t-test, it is possible only under the assumption of homogeneity of variances.}
\centering
\begin{tabular}[t]{ll}
\toprule
\textbf{Model} & \textbf{Equation}\\
\midrule
One-sample t-test & $d_c = \frac{t_c \times \mbox{SE}_b}{s} = t_c\sqrt{\frac{1}{n}}$\\
\cmidrule{1-2}
 & $d_c = \frac{t_c \times \mbox{SE}_b}{s_p}$\\
\cmidrule{2-2}
\multirow{-2}{*}{\raggedright\arraybackslash Paired t-test} & $d_{z_c} = \frac{t_c \times \mbox{SE}_b}{s_D} = t_c\sqrt{\frac{1}{n}}$\\
\cmidrule{1-2}
Between-sample t-test & $d_c = \frac{t_c \times \mbox{SE}_b}{s_p} = t_c\sqrt{\frac{1}{n_1} + \frac{1}{n_2}}$\\
\cmidrule{1-2}
Correlation test & $r_c = \frac{t_c}{\sqrt{n - 2 + t^2_c}}$\\
\cmidrule{1-2}
Correlation & $r_{z_c} = \frac{z_c}{\sqrt{n - 3}}$\\
\cmidrule{1-2}
Meta-analysis/Regression & $\beta_c = t_c \times \mbox{SE}_{\beta}$\\
\bottomrule
\end{tabular}
\end{table}

@@

\section{Examples in R}\label{examples-in-r}

@@

\section{References}\label{references}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-altoe2020enhancing}
Altoè, G., Bertoldo, G., Zandonella Callegher, C., Toffalini, E., Calcagnı̀, A., Finos, L., \& Pastore, M. (2020). Enhancing statistical inference in psychological research via prospective and retrospective design analysis. \emph{Frontiers in Psychology}, \emph{10}, 499756.

\bibitem[\citeproctext]{ref-apa2020publication}
American Psychological Association. (2020). \emph{Publication manual of the american psychological association} (7th ed.). American Psychological Association. \url{https://doi.org/10.1037/0000165-000}

\bibitem[\citeproctext]{ref-anvari2023not}
Anvari, F., Kievit, R., Lakens, D., Pennington, C. R., Przybylski, A. K., Tiokhin, L., Wiernik, B. M., \& Orben, A. (2023). Not all effects are indispensable: Psychological science requires verifiable lines of reasoning for whether an effect matters. \emph{Perspectives on Psychological Science}, \emph{18}(2), 503--507.

\bibitem[\citeproctext]{ref-bakan1967method}
Bakan, D. (1967). On method: Toward a reconstruction of psychological investigation. \emph{(No Title)}.

\bibitem[\citeproctext]{ref-borenstein2021introduction}
Borenstein, M., Hedges, L. V., Higgins, J. P., \& Rothstein, H. R. (2021). \emph{Introduction to meta-analysis}. John wiley \& sons.

\bibitem[\citeproctext]{ref-boring1919mathematical}
Boring, E. G. (1919). Mathematical vs. Scientific significance. \emph{Psychological Bulletin}, \emph{16}(10), 335.

\bibitem[\citeproctext]{ref-Bowley1928-yt}
Bowley, A. L. (1928). The standard deviation of the correlation coefficient. \emph{Journal of the American Statistical Association}, \emph{23}, 31. \url{https://doi.org/10.2307/2277400}

\bibitem[\citeproctext]{ref-byers2020building}
Byers-Heinlein, K., Bergmann, C., Davies, C., Frank, M. C., Hamlin, J. K., Kline, M., Kominsky, J. F., Kosie, J. E., Lew-Williams, C., Liu, L., et al. (2020). Building a collaborative psychological science: Lessons learned from ManyBabies 1. \emph{Canadian Psychology/Psychologie Canadienne}, \emph{61}(4), 349.

\bibitem[\citeproctext]{ref-chow1988significance}
Chow, S. L. (1988). Significance test or effect size? \emph{Psychological Bulletin}, \emph{103}(1), 105.

\bibitem[\citeproctext]{ref-cohen1994}
Cohen, J. (1994). The earth is round (p \textless{} .05). \emph{American Psychologist}, \emph{49}(12), 997--1003.

\bibitem[\citeproctext]{ref-cortina1997logic}
Cortina, J. M., \& Dunlap, W. P. (1997). On the logic and purpose of significance testing. \emph{Psychological Methods}, \emph{2}(2), 161.

\bibitem[\citeproctext]{ref-cumming2012statistical}
Cumming, G., Fidler, F., Kalinowski, P., \& Lai, J. (2012). The statistical recommendations of the american psychological association publication manual: Effect sizes, confidence intervals, and meta-analysis. \emph{Australian Journal of Psychology}, \emph{64}(3), 138--146.

\bibitem[\citeproctext]{ref-Fisher1915-ks}
Fisher, R. A. (1915). Frequency distribution of the values of the correlation coefficient in samples from an indefinitely large population. \emph{Biometrika}, \emph{10}, 507. \url{https://doi.org/10.2307/2331838}

\bibitem[\citeproctext]{ref-Fisher1921-qz}
Fisher, R. A. (1921). On the "probable error" of a coefficient of correlation deduced from a small sample. \emph{Metron}.

\bibitem[\citeproctext]{ref-funder2019evaluating}
Funder, D. C., \& Ozer, D. J. (2019). Evaluating effect size in psychological research: Sense and nonsense. \emph{Advances in Methods and Practices in Psychological Science}, \emph{2}(2), 156--168.

\bibitem[\citeproctext]{ref-Gelman2008-zp}
Gelman, A. (2008). Scaling regression inputs by dividing by two standard deviations. \emph{Statistics in Medicine}, \emph{27}, 2865--2873. \url{https://doi.org/10.1002/sim.3107}

\bibitem[\citeproctext]{ref-gigerenzer2004null}
Gigerenzer, G., Krauss, S., \& Vitouch, O. (2004). The null ritual. \emph{The Sage Handbook of Quantitative Methodology for the Social Sciences}, 391--408.

\bibitem[\citeproctext]{ref-Gross2023-fl}
Groß, J., \& Möller, A. (2023). A note on cohen's d from a partitioned linear regression model. \emph{Journal of Statistical Theory and Practice}, \emph{17}. \url{https://doi.org/10.1007/s42519-023-00323-w}

\bibitem[\citeproctext]{ref-hagen1997praise}
Hagen, R. L. (1997). \emph{In praise of the null hypothesis statistical test.}

\bibitem[\citeproctext]{ref-haig2017tests}
Haig, B. D. (2017). Tests of statistical significance made sound. \emph{Educational and Psychological Measurement}, \emph{77}(3), 489--506.

\bibitem[\citeproctext]{ref-Hedges1981-za}
Hedges, L. V. (1981). Distribution theory for glass's estimator of effect size and related estimators. \emph{Journal of Educational and Behavioral Statistics: A Quarterly Publication Sponsored by the American Educational Research Association and the American Statistical Association}, \emph{6}, 107--128. \url{https://doi.org/10.3102/10769986006002107}

\bibitem[\citeproctext]{ref-hedges1984estimation}
Hedges, L. V. (1984). Estimation of effect size under nonrandom sampling: The effects of censoring studies yielding statistically insignificant mean differences. \emph{Journal of Educational Statistics}, \emph{9}(1), 61--85.

\bibitem[\citeproctext]{ref-hodges1954matching}
Hodges, J., \& Lehmann, E. (1954). Matching in paired comparisons. \emph{The Annals of Mathematical Statistics}, \emph{25}(4), 787--791.

\bibitem[\citeproctext]{ref-jarke2022roadmap}
Jarke, H., Anand-Vembar, S., Alzahawi, S., Andersen, T. L., Bojanić, L., Carstensen, A., Feldman, G., Garcia-Garzon, E., Kapoor, H., Lewis, S., et al. (2022). A roadmap to large-scale multi-country replications in psychology. \emph{Collabra: Psychology}, \emph{8}(1), 57538.

\bibitem[\citeproctext]{ref-kirk1996practical}
Kirk, R. E. (1996). Practical significance: A concept whose time has come. \emph{Educational and Psychological Measurement}, \emph{56}(5), 746--759.

\bibitem[\citeproctext]{ref-kramer2014experimental}
Kramer, A. D., Guillory, J. E., \& Hancock, J. T. (2014). Experimental evidence of massive-scale emotional contagion through social networks. \emph{Proceedings of the National Academy of Sciences of the United States of America}, \emph{111}(24), 8788.

\bibitem[\citeproctext]{ref-krueger2001null}
Krueger, J. (2001). Null hypothesis significance testing: On the survival of a flawed method. \emph{American Psychologist}, \emph{56}(1), 16.

\bibitem[\citeproctext]{ref-lakens2013calculating}
Lakens, D. (2013). Calculating and reporting effect sizes to facilitate cumulative science: A practical primer for t-tests and ANOVAs. \emph{Frontiers in Psychology}, \emph{4}, 62627.

\bibitem[\citeproctext]{ref-lakens2021practical}
Lakens, D. (2021). The practical alternative to the p value is the correctly used p value. \emph{Perspectives on Psychological Science}, \emph{16}(3), 639--648.

\bibitem[\citeproctext]{ref-lakens2022sample}
Lakens, D. (2022). Sample size justification. \emph{Collabra: Psychology}, \emph{8}(1), 33267.

\bibitem[\citeproctext]{ref-mesquida2024effect}
Mesquida, C., \& Lakens, D. (2024). Is the effect large enough to matter? Why exercise physiologists should interpret effect sizes meaningfully: A reply to williams et al.(2023). \emph{Journal of Physiology}, \emph{602}(1).

\bibitem[\citeproctext]{ref-miller2017hypothesis}
Miller, J. (2017). Hypothesis testing in the real world. \emph{Educational and Psychological Measurement}, \emph{77}(4), 663--672.

\bibitem[\citeproctext]{ref-morris2002combining}
Morris, S. B., \& DeShon, R. P. (2002). Combining effect size estimates in meta-analysis with repeated measures and independent-groups designs. \emph{Psychological Methods}, \emph{7}(1), 105.

\bibitem[\citeproctext]{ref-moshontz2018psychological}
Moshontz, H., Campbell, L., Ebersole, C. R., IJzerman, H., Urry, H. L., Forscher, P. S., Grahe, J. E., McCarthy, R. J., Musser, E. D., Antfolk, J., et al. (2018). The psychological science accelerator: Advancing psychology through a distributed collaborative network. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(4), 501--515.

\bibitem[\citeproctext]{ref-nickerson2000null}
Nickerson, R. S. (2000). Null hypothesis significance testing: A review of an old and continuing controversy. \emph{Psychological Methods}, \emph{5}(2), 241.

\bibitem[\citeproctext]{ref-nunnally1960place}
Nunnally, J. (1960). The place of statistics in psychology. \emph{Educational and Psychological Measurement}, \emph{20}(4), 641--650.

\bibitem[\citeproctext]{ref-orben_crud_2020}
Orben, A., \& Lakens, D. (2020). Crud ({Re}){Defined}. \emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(2), 238--247. \url{https://doi.org/10.1177/2515245920917961}

\bibitem[\citeproctext]{ref-riesthuis2024simulation}
Riesthuis, P. (2024). Simulation-based power analyses for the smallest effect size of interest: A confidence-interval approach for minimum-effect and equivalence testing. \emph{Advances in Methods and Practices in Psychological Science}, \emph{7}(2), 25152459241240722.

\bibitem[\citeproctext]{ref-Satterthwaite1946-aq}
Satterthwaite, F. E. (1946). An approximate distribution of estimates of variance components. \emph{Biometrics Bulletin}, \emph{2}, 110. \url{https://doi.org/10.2307/3002019}

\bibitem[\citeproctext]{ref-serlin1985rationality}
Serlin, R. C., \& Lapsley, D. K. (1985). \emph{Rationality in psychological research: The good-enough principle.}

\bibitem[\citeproctext]{ref-sirois2023pupil}
Sirois, S., Brisson, J., Blaser, E., Calignano, G., Donenfeld, J., Hepach, R., Hochmann, J.-R., Kaldy, Z., Liszkowski, U., Mayer, M., et al. (2023). The pupil collaboration: A multi-lab, multi-method analysis of goal attribution in infants. \emph{Infant Behavior and Development}, \emph{73}, 101890.

\bibitem[\citeproctext]{ref-szucs2017empirical}
Szucs, D., \& Ioannidis, J. P. (2017). Empirical assessment of published effect sizes and power in the recent cognitive neuroscience and psychology literature. \emph{PLoS Biology}, \emph{15}(3), e2000797.

\bibitem[\citeproctext]{ref-transue2019apa}
Transue, B. (2019). \emph{APA style 7th edition}.

\bibitem[\citeproctext]{ref-Viechtbauer2007-tq}
Viechtbauer, W. (2007). Approximate confidence intervals for standardized effect sizes in the two-independent and two-dependent samples design. \emph{Journal of Educational and Behavioral Statistics: A Quarterly Publication Sponsored by the American Educational Research Association and the American Statistical Association}, \emph{32}, 39--60. \url{https://doi.org/10.3102/1076998606298034}

\bibitem[\citeproctext]{ref-Viechtbauer2015-tn}
Viechtbauer, W., López-López, J. A., Sánchez-Meca, J., \& Marín-Martínez, F. (2015). A comparison of procedures to test for moderators in mixed-effects meta-regression models. \emph{Psychological Methods}, \emph{20}, 360--374. \url{https://doi.org/10.1037/met0000023}

\bibitem[\citeproctext]{ref-weiss2014spatial}
Weiss, A. H., Biron, T., Lieder, I., Granot, R. Y., \& Ahissar, M. (2014). Spatial vision is superior in musicians when memory plays a role. \emph{Journal of Vision}, \emph{14}(9), 18--18.

\bibitem[\citeproctext]{ref-Welch1947-wh}
Welch, B. L. (1947). The generalization of {``student's''} problem when several different population variances are involved. \emph{Biometrika}, \emph{34}, 28. \url{https://doi.org/10.2307/2332510}

\bibitem[\citeproctext]{ref-wilson2020science}
Wilson, B. M., Harris, C. R., \& Wixted, J. T. (2020). Science is not a signal detection problem. \emph{Proceedings of the National Academy of Sciences}, \emph{117}(11), 5559--5567.
